A Decentralized Pub/Sub System for Trusted Machine Economy

### 2020-04-28 paper.tex
Add requirements of DM in Introduction

\section{Introduction}
%TODO: cite examples
In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings a potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving} and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. And data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform.

The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency. In the publish-subscribe system, a broker is the bridge to meet publishers and subscribers. Broker is a centralized group that arrange the communication between the publishers and subscribers. However, the centralized architecture brings potential vulnerabilities and security issues:

>>>>

\section{Introduction}
%TODO: cite examples
In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings a potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers and data consumers meet.

Among the challenges of data marketplace\cite{BigDataMarket}, our proposed decentralized data marketplace in\cite{MyDataMarketplace} focuses on the following issues:

\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of data marketplace should scale with the massive amount of participants. 2) Keys managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. 1) Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leaked within the subscription history.
	\item \textbf{Economics Incentive}. The economics incentives can encourage the data providers to participate the system and pay more attention on the quilatiy control. 
\end{itemize}

% may be removed
The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency. In the publish-subscribe system, a broker is the bridge to meet publishers and subscribers. Broker is a centralized group that arrange the communication between the publishers and subscribers. However, the centralized architecture brings potential vulnerabilities and security issues:
